---
title: "Detroit"
author: "Jonathan Mishory"
date: "2/11/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(tidyverse)
library(lubridate)



devtools::install_github("cmf-uchicago/cmfproperty", force = TRUE)

library(cmfproperty)
```

Template file. Code will be included in folded blocks in the output to facilitate grading. Please knit this file and commit both the rmd and the html output. If you add external files to your analysis, please commit them to the files folder in this repository. NOTE: please do not commit large (15MB+) files to GitHub. Instead please denote the origin of the files in your code. 
install.packages("RSQLite")
```{r}

con <- DBI::dbConnect(RSQLite::SQLite(), "GitHub/detroit-jonathanmishory/database/detroit.sqlite")
# sales tbl
dplyr::tbl(con, 'sales')
# convert to tibble
sales <- dplyr::tbl(con, 'sales') %>% dplyr::collect()
# sql query
dplyr::tbl(con, 'sales') %>% count(year(sale_date))
sales %>% count(year(sale_date))
dplyr::tbl(con, 'sales') %>% count(year(sale_date)) %>% show_query()

sales <- sales %>%
  rename(parcel_number = parcel_num)

# sales tbl
dplyr::tbl(con, 'foreclosures')
# convert to tibble
foreclosures <- dplyr::tbl(con, 'foreclosures') %>% dplyr::collect()

# foreclusures tbl
dplyr::tbl(con, 'foreclosures')
# convert to tibble
foreclosures <- dplyr::tbl(con, 'foreclosures') %>% dplyr::collect()
foreclosures <- foreclosures %>%
  rename(parcel_number = prop_parcelnum)
# parcels tbl
dplyr::tbl(con, 'parcels')
# convert to tibble
parcels <- dplyr::tbl(con, 'parcels') %>% dplyr::collect()


# parcels_historic tbl
dplyr::tbl(con, 'parcels_historic')
# convert to tibble
parcels_historic <- dplyr::tbl(con, 'parcels_historic') %>% dplyr::collect()

# blight tbl
dplyr::tbl(con, 'blight')
# convert to tibble
blight <- dplyr::tbl(con, 'blight') %>% dplyr::collect()

# assessments tbl
dplyr::tbl(con, 'assessments')
# convert to tibble
assessments <- dplyr::tbl(con, 'assessments') %>% dplyr::collect()
```
sale <- "sales"


```{r}
summary(sales$sale_price)
#Mean 22924
summary(parcels$sale_price)
#mean 42154
summary(parcels$assessed_value)
#mean 24503
summary(parcels$taxable_value)
#mean 13600


#There is a noticeable difference between the mean assessed value and the mean taxable value. This is inline with the literature about Detroit housing, as property taxes assessments have been reported as being illegally inflated in order for the government to gain more revenue from property taxes. 
```


```{r}



mergedsales<-merge(x=sales,y=parcels,by="parcel_number",all.x=TRUE)

remove(ratios)

mergedsales$SALE_YEAR <- year(mergedsales$sale_date.x)

#ratios <-
# cmfproperty::reformat_data(
#  data = "mergedsales",
# sale_col = "sale_price.x",
#assessment_col = "assessed_value",
#sale_year_col = "Year",
#)
#subscript out of bounds error
```

```{r}


lm1 <- lm(sale_price.x ~ assessed_value, data = mergedsales)
summary(lm1)
#Sale Price vs. Assessed value
lm2 <- lm(sale_price.x ~ total_square_footage, data = mergedsales)
summary(lm2)
#Sale price vs. Square Footage
lm3 <- lm(sale_price.x ~ is_improved, data = mergedsales)
summary(lm3)
#This is a categorical variable for if there are improvements

#All regression terms are statistically significant. However they all have a low R-Square value, meaning there is a weak correlation. 


ggplot(mergedsales,aes(sale_price.x,assessed_value)) + geom_point()

```

```{r}
foreclosures$foreclosure_count <- rowSums( foreclosures[,3:20], na.rm = T )


mergedforeclosures <-merge(x=foreclosures,y=parcels,by="parcel_number",all.x=TRUE)


lm4 <- lm(foreclosure_count ~ assessed_value, data = mergedforeclosures)
summary(lm4)
#Foreclosure count vs. Assessed Value
lm5 <- lm(foreclosure_count ~ total_square_footage, data = mergedforeclosures)
summary(lm5)
#Foreclosure count vs. Square footage
lm6 <- lm(foreclosure_count ~ is_improved, data = mergedforeclosures)
summary(lm6)
#Foreclosure count vs. categorical variable- is improved. 

#All regression terms are statistically significant. However they all have a low R-Square value, meaning there is a weak correlation. 


ggplot(mergedforeclosures,aes(foreclosure_count,assessed_value)) + geom_point()

```








